Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-21 paper/paper.tex
More changes to 5.4

In order to compare the efficiency of our algorithms, we counted the number of times
each algorithm achieved the best result for all simulated applications, deadlines
and budgets. Table~\ref{tab:num-dags-pareto} shows these summary values for 
Pareto-distributed workflows. Note that all algorithms that achieve the best 
result are credited, so the sum for a given application can be greater than the
total number of scenarios. These results depend on the metric: number of
workflows completed does not count the priorities or sizes of workflows, which
means that it happens more often that all the algorithms achieve the same best
result. However, it does not mean that all algorithms complete the same
workflows: that is why the values in (a), (b) and (c) are different. The 
exponential score and total amount of computing time completed give the same
rankings, since in our test ensembles larger workflows were given higher
priorities. It can be observed based on the sampled problem space that the
workflow-aware algorithms achieve highest score in $\sim$2--3 times more cases
than the simple DPDS algorithm which does not take into account workflow 
structure or size. SPSS performs the best in $\sim$20\% more cases than WA-DPDS,
including the Montage and CyberShake ensembles, for which SPSS does not 
perform as well as DPDS and WA-DPDS.

Similar results were achieved for ensembles consisting of workflows of equal
size. Summary of these results is shown in Table~\ref{tab:num-dags-equal}.
Again, we can see that static SPSS algorithm performed better for coarse-grained
workflows (LIGO, Epigenomics, SIPHT). The differences between algorithm scores
are smaller since the workflows have equal size thus rejecting one workflow
does not help to complete more work in any case.

Fig.~\ref{fig:budgets} shows the same data for SIPHT ensemble from another
perspective. It helps answer the question: given a deadline, how many workflows
can be finished when we increase the budget. In Fig.~\ref{fig:budgets}(a) the
growth is super-linear, what results from the distribution of workflow sizes in
the ensemble (see Fig.~\ref{fig:ensemble-distribution}). For ensemble of equal
size workflows (see Fig.~\ref{fig:budgets}(b)) the growth is nearly linear. It
can be also observed that static algorithms give better results for smaller
budgets, while dynamic algorithms for larger ones.

>>>>

In order to compare the efficiency of our algorithms, we counted the number of times
each algorithm achieved the best result for all simulated applications, deadlines
and budgets. Table~\ref{tab:num-dags-pareto} shows these summary values for 
Pareto-distributed workflows. Note that all algorithms that achieve the best 
result are credited, so the sum for a given application can be greater than the
total number of scenarios. These results depend on the metric: number of
workflows completed does not count the priorities or sizes of workflows, which
means that it happens more often that all the algorithms achieve the same best
result. However, it does not mean that all algorithms complete the same
workflows: that is why the values in (a), (b) and (c) are different. The 
exponential score and total amount of computing time completed give the same
rankings, since in our test ensembles larger workflows were given higher
priorities. It can be observed based on the sampled problem space that the
workflow-aware algorithms achieve the highest score in $\sim$2--3 times more 
cases than the simple DPDS algorithm, which does not take into account workflow 
structure or size. SPSS performs the best in $\sim$20\% more cases than WA-DPDS,
including the Montage and CyberShake ensembles, for which SPSS does not 
perform as well as WA-DPDS.

Similar results were achieved for ensembles consisting of workflows of equal
size. A summary of these results is shown in Table~\ref{tab:num-dags-equal}.
Again, we can see that the static SPSS algorithm performed better for coarse-grained
workflows (LIGO, Epigenomics, SIPHT). The differences between algorithm scores
are smaller since the workflows have equal size, therefore rejecting a particular
workflow does not enable the algorithms to complete any other workflows.

Fig.~\ref{fig:budgets} shows the same data for the SIPHT ensemble from another
perspective. It helps answer the question: Given a deadline, how many workflows
can be finished when we increase the budget? In Fig.~\ref{fig:budgets}(a) the
growth is super-linear, which results from the Pareto-like distribution of 
workflow sizes in the ensemble (see Fig.~\ref{fig:ensemble-distribution}). 
For ensembles of constant size workflows (see Fig.~\ref{fig:budgets}(b)) 
the growth is nearly linear.
